Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-23 ms.qmd
Adding VR table with some formatting

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage)

@@

   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)

  # Save model1.2
  saveRDS(model3.2, file = "./output/models/lnVRQ10_3.2")
  saveRDS(model3.2_bayes, file = "./output/models/lnVRQ10_3.2_bayes")

@@

>>>>

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt)

@@

   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
      summary(model3.2_bayes)                            
  # Save model1.2
  saveRDS(model3.2, file = "./output/models/lnVRQ10_3.2")
  saveRDS(model3.2_bayes, file = "./output/models/lnVRQ10_3.2_bayes")

@@

```{r}
#| label: tbl-tabs1
#| tbl-cap: Model estimates, standard error, and 95% credible intervals

 # Extract the fixed / population-level effect summaries of the posterior
    fixed <- summary(model3.2_bayes)$fixed[,1:4]
    fixed <- cbind(Parameter = rownames(fixed), fixed)
  rownames(fixed) <- NULL

 # Extract the random effect summaries of the posteriors (SDs)
  random <- plyr::ldply(summary(model3.2_bayes)$random)[,1:5]
  colnames(random)[1] <- "Parameter"

# Headers for the table to indicate fixed and random effects
  fixed_head <- c("Fixed Effects", rep(" ", 4))
  random_head <- c("Random Effects", rep(" ", 4))

# Create the table
  tabs1 <- rbind(fixed, random)
  gt(tabs1) %>%  fmt_number(
    columns = 2:5,
    decimals = 2
  ) %>% tab_row_group(label = "Fixed Effects", rows = 1:7) %>% tab_row_group(label = "Random Effects", rows = 8:11)
```
